\documentclass[]{danpilch-resume}
\usepackage{fancyhdr}

% ===== Add pandoc compatibility code here =====
\usepackage{hyperref} % For link preservation
% =======================================

\pagestyle{fancy}
\fancyhf{}

\begin{document}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     LAST UPDATED DATE
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% \lastupdated

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     TITLE NAME
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\namesection{Daniel Pilch}{ %\urlstyle{same}\href{https://www.linkedin.com/in/danpilch/}{linkedin}| \href{https://github.com/danpilch}{Github}\\
\href{mailto:danielpilch@hotmail.co.uk}{danielpilch@hotmail.co.uk} | \href{tel:+447716979933}{+44771697993} | UK/Remote
}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     COLUMN ONE
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{minipage}[t]{0.60\textwidth}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     EXPERIENCE
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Experience}
\runsubsection{Community.com}
\descript{| Staff Platform Engineer }
\location{September 2020 – Present | Remote, USA/UK }
\vspace{\topsep} % Hacky fix for awkward extra vertical space
\begin{tightemize}
\item Platform strategy: Lead the strategy, architecture and management of Community's infrastructure and platform systems.
\item Platform migration: Successfully migrated Community from Mesos to Kubernetes in AWS, ensuring parallel availability of both platforms during migration.
\item Reduced complexity and costs while keeping within Community's 99.5\% uptime SLA.
\item Operational cost management: Reduced overall cloud spend by 33\% (\$320,000) per year by introducing policy, spend controls and rightsizing workloads.
\item Built and maintained tooling in golang, python and Elixir.
\end{tightemize}
\sectionsep

\runsubsection{Nomura}
\descript{| VP Engineering }
\location{May 2020 – August 2020 | Remote, UK}
\begin{tightemize}
\item Planned and provisioned core banking network infrastructure routing via AWS DirectConnect and VPC peering.
\item Provisioned AWS accounts for business units, focusing on account hardening, IAM, security and networking.
\end{tightemize}
\sectionsep

\runsubsection{Westpac New Zealand}
\descript{| DevOps / Data Engineer }
\location{December 2018 – November 2019 | Auckland, New Zealand}
\begin{tightemize}
\item Led the development of a fraud data processing platform using Kafka, Spark, Hadoop, Hive, and Airflow on Kubernetes.
\item Integrated mainframe IBM MQ queues with Kafka for real-time transaction data streaming.
\end{tightemize}
\sectionsep

\runsubsection{Bitcoin.com.au}
\descript{| DevOps Engineer }
\location{November 2017 – October 2018 | Melbourne/Remote, Australia}
\begin{tightemize}
\item Migrated bitcoin.com.au's entire platform softare entire stack to AWS using Terraform, Ansible and Docker.
\item Migrated all software repositories and CI pipelines from Bitbucket to GitLab.
\end{tightemize}
\sectionsep

\runsubsection{PPL UK}
\descript{| DevOps Engineer }
\location{July 2016 – October 2017 | London, UK}
\begin{tightemize}
\item Established a DevOps culture and managed projects involving Apache Hadoop, AWS CloudFormation, and Docker.
\end{tightemize}
\sectionsep

\runsubsection{Incopro}
\descript{| DevOps Engineer }
\location{May 2013 – July 2016 | London, UK}
\begin{tightemize}
\item Founding member of the company.
\item Automated provisioning and deployments on 500+ base metal servers using Ansible.
\item Managed web scraping software that scraped over 1000 websites for content and trademark protection.
\end{tightemize}
\sectionsep

\runsubsection{Warner Bros.}
\descript{| Anti-Piracy Intern }
\location{September 2011 – September 2012 | London, UK}
\begin{tightemize}
\item Managed data centre infrastructure for content protection activities through building web scrapers and DMCA content takedown.
\end{tightemize}
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     COLUMN TWO
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\end{minipage}
\hfill
\begin{minipage}[t]{0.33\textwidth}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     EDUCATION
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Education}

\subsection{University of Portsmouth}
\descript{Computer Science BSc (Hons) | (1st Class)}
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     SKILLS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Skills}
\subsection{Programming}
\location{10+ years:}
Python \textbullet{} Bash \\
\location{5+ years:}
Golang \\
\location{2+ years:}
Ruby \textbullet{} Elixir \\
\sectionsep

\subsection{Core Technology}
Kubernetes \textbullet{} AWS \textbullet{} Linux \\
Terraform \textbullet{} Ansible \textbullet{} Packer \\
OpenVPN \textbullet{} Tailscale \textbullet{} Docker \\
Git/Github \textbullet{} AI (openai, huggingface, Ollama etc.) \\
\sectionsep

\subsection{Database Technology}
PostgreSQL \textbullet{} MariaDB \textbullet{} Athena \\
DynamoDB \textbullet{} Trino \textbullet{} Athena \\ 
RabbitMQ \textbullet{} Prometheus \\
\sectionsep

\subsection{API Gateways and Proxies}
HAProxy \textbullet{} Envoy \textbullet{} Kong \\
\sectionsep

\subsection{Vendor Technology}
Temporal \textbullet{} Okta \textbullet{} Appsignal \\
NewRelic \textbullet{} SumoLogic \textbullet{} PlanetScale \\
Cloudflare \textbullet{} PagerDuty \textbullet{} Twilio \\
Databricks
\sectionsep

\subsection{Soft Skills}
People Management \textbullet{} Project Management \textbullet{} Engineering Leadership \\
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     Personal
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Personal Life}
Outside of work, I enjoy exercise, playing guitar, travel, and spending time with my wife Laura and Golden Retriever Lily.
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     LINKS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Links}
Github:// \href{https://github.com/danpilch}{\bf danpilch} \\
LinkedIn://  \href{https://www.linkedin.com/in/danpilch}{\bf danpilch}
\sectionsep

\end{minipage}
\end{document}  \documentclass[]{article}
