\documentclass[]{resume}
\usepackage{fancyhdr}

% ===== Add pandoc compatibility code here =====
\usepackage{hyperref} % For link preservation
% =======================================

\setcounter{secnumdepth}{0}
\pagestyle{fancy}
\fancyhf{}

\begin{document}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     TITLE NAME
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\namesection{Daniel Pilch}{ %\urlstyle{same}\href{https://www.linkedin.com/in/danpilch/}{linkedin}| \href{https://github.com/danpilch}{Github}\\
\href{mailto:danielpilch@hotmail.co.uk}{danielpilch@hotmail.co.uk} | \href{tel:+447716979933}{+44771697993} | London UK / Remote
}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     COLUMN ONE
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{minipage}[t]{0.65\textwidth}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     SUMMARY
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Summary}
Engineering leader and hands-on IC with over 13 years experience designing, scaling, and managing distributed systems. Currently leading platform engineering at Community.com, driving infrastructure, AI, and operational strategy. Proven track record of building resilient platforms, optimizing cloud and compute costs, and aligning engineering roadmaps with business objectives. Deep expertise in Kubernetes, cloud-native architecture, and AI/ML infrastructure. Passionate about solving complex technical challenges, fostering high-performing teams, and delivering scalable, reliable solutions.
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     EXPERIENCE
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Experience}
\runsubsection{Community.com}
\descript{| Staff Platform Engineer }
\location{September 2020 – Present | Remote, USA/UK }
\vspace{\topsep} % Hacky fix for awkward extra vertical space
\begin{tightemize}
\item Lead strategy, architecture, and operations for the platform team, collaborating closely with the CTO and VP of Architecture to drive scalable, cost-efficient infrastructure solutions.
\item Spearheaded the migration from Apache Mesos to Kubernetes on AWS, ensuring high availability and minimal disruption during the transition.
\item Developed an AI-driven On-Call Slack Bot in Go that streamlined access to community runbooks and on-call information; facilitating a 50\% reduction in manual lookup times during active incidents, freeing up valuable resources.
\item Built an AI-powered On-Call Slack Bot in Go, integrating with Community’s runbooks and on-call data to streamline incident resolution.
\item Optimized cloud infrastructure, maintaining a 99.5\% uptime SLA while simplifying systems and reducing complexity.
\item Achieved an average 33\% annual cloud cost reduction (\$320,000) by implementing spend controls, policies, and workload rightsizing.
\end{tightemize}
\sectionsep

\runsubsection{Nomura}
\descript{| VP Cloud Engineering }
\location{May 2020 – August 2020 | Remote, UK}
\begin{tightemize}
\item Led the design and provisioning of core banking network infrastructure at Nomura, implementing AWS DirectConnect, BGP, and VPC peering. Utilized Terraform, Ansible, and Python to automate deployment, ensuring secure, high-performance cloud connectivity for critical financial operations.
\end{tightemize}
\sectionsep

\runsubsection{Westpac New Zealand}
\descript{| DevOps \& Software Engineer }
\location{December 2018 – November 2019 | Auckland, New Zealand}
\begin{tightemize}
\item Designed and implemented a fraud data processing platform at Westpac New Zealand, leveraging Kafka, Spark, Hadoop, Hive, and Airflow on Kubernetes. Collaborated with the Head of Engineering to integrate IBM MQ mainframe queues with Kafka for real-time fraud detection and transaction monitoring.
\end{tightemize}
\sectionsep

\runsubsection{Bitcoin.com.au}
\descript{| DevOps Engineer }
\location{November 2017 – October 2018 | Melbourne/Remote, Australia}
\begin{tightemize}
\item Led the migration of Bitcoin.com.au’s entire platform to AWS with Terraform, Ansible, and Docker, while rewriting their fiat-to-Bitcoin payment gateway for a more robust and scalable system.
\end{tightemize}
\sectionsep

\runsubsection{PPL UK}
\descript{| DevOps Engineer }
\location{July 2016 – October 2017 | London, UK}
\begin{tightemize}
\item Drove DevOps innovation at PPL UK as part of their digital transformation programme, working closely with the CTO and Head of Architecture to revolutionize infrastructure with Apache Hadoop, AWS CloudFormation, and Docker.
\end{tightemize}
\sectionsep

\runsubsection{Incopro}
\descript{| Platform \& Software Engineer }
\location{May 2013 – July 2016 | London, UK}
\begin{tightemize}
\item Founding member of Incopro, automating deployments for 500+ servers with Ansible and scaling web scraping to protect content and trademarks across 1,000+ sites.
\end{tightemize}
\sectionsep

%\runsubsection{Warner Bros.}
%\descript{Anti Piracy Engineer}
%\location{September 2011 - September 2012 | London, UK}
%\begin{tightemize}
%\item Enhanced content protection at Warner Bros. by developing web scraping tools to combat piracy.
%\end{tightemize}
%\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     COLUMN TWO
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\end{minipage}
\hfill
\begin{minipage}[t]{0.33\textwidth}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     SKILLS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Technical Skills}
\subsection{Programming}
Python, Go, Ruby, Shell derivatives (Bash etc.)
\sectionsep

\subsection{Leadership \& Management}
Engineering Leadership, People Management, Project Management
\sectionsep

\subsection{Infrastructure (IaC) \& Cloud}
Kubernetes, Docker, Helm, Containerd, Podman, AWS (many services), GCP, Azure, Linux/UNIX, Terraform, Ansible, Packer, Vagrant
\sectionsep

\subsection{Networking \& Security}
OpenVPN, WireGuard, Tailscale, HAProxy, Envoy, Kong, IAM, VPC, Cloudflare
\sectionsep

\subsection{Databases \& Messaging}
PostgreSQL, Cassandra, MariaDB, DynamoDB, Trino, Athena, RabbitMQ, Elasticache, Elasticsearch, Redis, Prometheus
\sectionsep

\subsection{DevOps \& Monitoring}
Git, Concourse, NewRelic, SumoLogic, AppSignal, PagerDuty, Jenkins
\sectionsep

\subsection{Machine Learning \& AI}
PyTorch, TensorFlow, FastAPI, OpenAI, Hugging Face, LlamaIndex, LLamafile, Ollama, Databricks, Temporal
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     EDUCATION
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Education}

\subsection{University of Portsmouth}
\descript{Computer Science BSc (Hons) | (1st Class)}
\sectionsep


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     Personal
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Personal Life}
Outside of work, I enjoy exercise, playing guitar, travel, and spending time with my wife Laura and Golden Retriever Lily.
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     LINKS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Links}
Github:// \href{https://github.com/danpilch}{\bf danpilch} \\
LinkedIn://  \href{https://www.linkedin.com/in/danpilch}{\bf danpilch}
\sectionsep

\end{minipage}
\end{document}  \documentclass[]{article}
